THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@

>>>>

Aspects of simulation of signal production are studied based on generators that simulate the interactions of quarks and gluons taking 
into account the probability distributions of each type of particle. These are packages of software that are controlled with 
configuration files that define various aspects such as decay channels, energy in the center of mass and refinements in the development 
of the jets that are generated by the Strong interaction of the quarks. The reconstruction and selection of tH events requires the use 
of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and neutral particles 
starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and hadrons, 
whichThey have a life time that allows them to leave the interaction region. These particles are used to identify the production of the 
top and the Higgs. In the case of the top, it usually decays to a cuark b and a boson W. Subsequently the W decays to two Leptons or two 
quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction can be done by studying the 
distributions of transverse momentum, the angular distributions of the different particles, and others properties.

@@

The expected results of this project are the following:
• Improve data adjustments and study the effects of uncertainties.
• Improve the sensitivity to the tH signal in the data of the second CMS run.
• Limit calculations in the effective section incorporating data from the second
run of the LHC.
• Calculate projections of signal sensitivity for the different phases of the LHC.
